Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-29 latex/afm-cs-main.tex
Rework nesta part.
Updates from Overleaf

Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with to NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
\end{equation*}

@@

Next, using a cross-correlation alignment technique
% discussed in Section~\ref{sec:align},
we aligned the master image with a sub-slice of each of
the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
computed the PSNR and SSIM. These results are shown in
Fig.~\ref{fig:rast_aligned_1}, which again shows the errors between the
aligned master and the remaining 6 images. Although the situation is improved
compared to the un-aligned images, there is still noticable stretching,
particularly in the $Y$-direction. Notably, with the alignment technique,
the SSIM lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99 and appears more stable in time.

@@

Th PSNR and SSIM metrics only assess the similarity of two images.
However, in AFM imaging, pure image quality is not the
only concern, particularly for delicate samples. What is needed is a figure of
merit for how much damage was done to specimen during the imaging process. While
this is not really a concern while imaging a hard calibration grating, it plays
a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
damage occurs while scanning into an uphill region, which results in a positive
deflection signal. The actual damage done by a given $Z_d$ will depend on the
spring constant of the cantilever and the softness of the specimen. Nonetheless,
we can use the positive deviations of $Z_d$ as a relative measure of damage
between different scan speeds or scanning methods, for a given cantiliver and
specimen. This motivates a metric we term the relative damage index (RDI), which
we define as
\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
  I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
\end{align}
where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
The RDI is basically the power in positive deflection. By excluding negative
values of the deflection, we do not penalize the CS algorithm while it is
re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
which we do want to penalize. This is illustrated in
Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
tuned controller. Only deflection signals in the red-shaded region will be
penalized by the RDI.

>>>>

Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
\end{equation*}

@@

Next, using a cross-correlation alignment technique
% discussed in Section~\ref{sec:align},
we aligned the master image with a sub-slice of each of
the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
computed the PSNR and SSIM. These results are shown in
Fig.~\ref{fig:rast_aligned_1}, which again shows the errors between the
aligned master and the remaining 6 images. Although the situation is improved
compared to the un-aligned images, there is still noticeable stretching,
particularly in the $Y$-direction. Notably, with the alignment technique,
the SSIM lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99 and appears more stable in time.

@@

Th PSNR and SSIM metrics only assess the similarity of two images.
However, in AFM imaging, pure image quality is not the
only concern, particularly for delicate samples. What is needed is a figure of
merit for how much damage was done to specimen during the imaging process. While
this is not really a concern while imaging a hard calibration grating, it plays
a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
damage occurs while scanning into an uphill region, which results in a positive
deflection signal. The actual damage done by a given $Z_d$ will depend on the
spring constant of the cantilever and the softness of the specimen. Nonetheless,
we can use the positive deviations of $Z_d$ as a relative measure of damage
between different scan speeds or scanning methods, for a given cantilever and
specimen. This motivates a metric we term the relative damage index (RDI), which
we define as
\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
  I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
\end{align}
where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
The RDI is basically the power in positive deflection. By excluding negative
values of the deflection, we do not penalize the CS algorithm while it is
re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
which we do want to penalize. This is illustrated in
Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
tuned controller. Only deflection signals in the red-shaded region will be
penalized by the RDI.
